Application of convolutional neural networks in optical text recognition to junk data filtering

### 2021-04-22 tex/paper/OMFI2021_Razumov_paper.tex
Figures were justified
Figures were justified in accordance with textwidth.
Paper was updated
Text was brushed further. Some issues were coloured by red.

\section{Methodology}
\subsection{Statement of the problem}
Let's consider a set of objects $ X = X_L \cup X_T$, where
$X_L$ is training sample,
$X_T$ is test sample,
$Y$ is set of valid responses. Also, assume that there is an objective function $g: X \rightarrow Y$, whose values are known only on the set $X_L$. Let the data be distributed according to some unknown distribution $P (x,y) = P(x) P (y|x)$, with some loss function given
$$
R(g(x), y) = 
\begin{cases} 
\phantom{>}0, & y = g(x), \\
> 0, & y \neq g(x).
\end{cases}
$$
In accordance with the principle of minimizing empirical risk, the loss function is used to be minimazied. In other words a decision function $g(x)$, which on average will lead to the smallest error is determined. Formally, one need to solve the minimization problem as follows
$$
g(x) = \operatorname*{argmin}_{f: X \rightarrow Y} E_{X,Y} R(f(x), y).
$$
To state the problem of junk data filtration, the set $Y$ consists of two elements $\{0, 1\}$, where $0$ and $1$ are desirable and undesirable data, respectively. Due to the roughness of the discrete computing methods $R = P[0, 1]$ is usually used in practice. Thus,the result of the classifier $r' = r(x)$ belongs to the desired class with a given threshold probability $\alpha$, which minimizes the error of the first and second kind.

@@

\subsection{Text preprocessing}
Since the text has a very heterogeneous structure and a single word can be written in many different ways (different font, encoding, case, etc.), but still have the same meaning, different methods of preprocessing the text or a combination of them are used.
The first step is to parse the text and decode it into the specified encoding. Then the conversion to the lower (or upper) case, removing unnecessary spaces, indents. The characters are replaced according to the specified rule. After that, the following methods are applied:

\subsubsection*{\it\,Stop words}
The text often contains many characters that do not carry a semantic load for the general meaning (two spaces, paragraph indentation), as well as stop words.
Stop words are words in any language that don't add much meaning to a sentence. Often, stop words include punctuation marks, pronouns, and prepositions. Often, spammers use them to make texts noisy in order to hide the spam content of the message. Since they can be safely ignored without sacrificing the meaning of the sentence, classification tasks often resort to removing them from the original message.

\subsubsection{\it\,Stemming and lemmatization}
Usually texts contain different grammatical forms of the same word, and may also contain the same root words. Using different algorithms, lemmatization and stemming aim to reduce all occurring word forms to a single, normal dictionary form.

Stemming is a crude heuristic process which cuts off "extra" from the word root, often resulting in a loss of word-formation suffixes. The main problem encountered when using stemming is the processing of words which, when forming different grammatical forms, change not only the ending, but also the base of the word. For example, the noun "cat" in the accusative and genitive plural has the form "cats. Because of such fluent vowels, a streamer must either ignore such forms, truncating "cats" to "koshk" and losing some of the word forms, or truncate the word to an unchangeable stem, obtaining "kosh," which can then lead to a complete loss of context. To minimize the negative consequences of too aggressive truncation of words by the streamer, it is necessary to perform memming of the searched keyword, and then compare the result with the output of the streamer for each of the words in the processed text. Even so, you will come across stems for entirely unrelated words.

Lemmatization is a more subtle process, which uses dictionary and morphological analysis to reduce a word to its canonical form (lemma). However, it applies simplistic word analysis without considering the context. This leads to ambiguities in determining parts of speech. For example, the lemmatization of the words in the phrase "we dig a hole" will yield two lemmatization options for the second word: the noun swarm and the verb dig. This ambiguity cannot be resolved without involving the morphological analyzer.

As a rule, lemmatization gives the most accurate results, and this is the approach used in the work.

\subsection{Text vectorization}
Modern machine learning algorithms cannot directly work with raw text, so it is necessary to build a text mapping to a vector space. This is called feature extraction. Let's consider several approaches for constructing this mapping.

\subsubsection{\it\,Bag of words}
The "bag of words" model is a simplified representation of textual information used in natural language processing and information retrieval tasks. In this model, the text is represented as a bag (multiset) of its words or phrases in the case of combinations of terms, ignoring grammar and in some cases even word order, but preserving multiplicity. Each such term (word or phrase) is assigned a number. In this case, the text is defined by the vector $x=(x_1,..., x_N)^T$, where $N$ is the dimension from the finite dictionary $X_L$ consisting of unique terms of the training sample. The following options for defining $x_i$ are possible
\begin{itemize}
\item Boolean weight equals $1,$ if element exists in a message or 
$0,$ else.
\item The number of occurrences of the $i$--th term in the text is 
$x_i = n_i.$
\item Term frequency is $x_i = n_i\left(\sum\limits_{k=1}^i n_k\right)^{-1}.$
\end{itemize}
To determine $x_i$, the frequency of the term is selected.

\subsubsection{Word2Vec}
The main problem with BOW is the loss of context between words. Since in natural language, the permutation of even two words of a sentence can completely change its meaning, this classification approach may have low accuracy.

Word2Vec is a text vectorization tool that takes into account the contextual relationship between words. The algorithm is based on such methods as huffman binary tree, skip-gram, negative sampling. The main problem with Word2Vec is finding the context for rare words.

\subsubsection{Fast Text}
FastText is a Word2Vec extension proposed by Facebook in 2016. Instead of entering individual words into a neural network, Fast Text splits the words into several n-grams (proverbs). For example, the trigrams for the word "apple" --- are "app", "ppl", and "pll" (excluding the beginning and end of word boundaries). The vector for the word "apple" is formed by the sum of all n-grams. After training the neural network, we will have embedding words for all n-grams from the training dataset.
With this approach, the algorithm becomes more sensitive to rare words, since it is very likely that some of their n-grams are also present in other words. It takes longer to train the Fastext model, but it works better than Word2Vec and allows you to correctly represent rare words.

\subsection{Text classification}
After vectorizing the text, we must construct a transformation from a set of features to a set of classifiable objects $g: X \rightarrow Y.$
According to the article [twitter threshold p. 4.6], unique points were marked by bins and the optimal threshold accuracy $ \ alpha = 0.75$ was calculated, which provides optimal pressision and recall for our model and minimizes the error variance.

\subsubsection{Logistic regression}
The commonly used approach in the classification is the logistic regression method
$$
g(x) = \left(1 + \exp{ \left( \sum_{i=0}^n w_i x_i  \right) }\right)^{-1},
$$
where $\mathbf{w}=(w_1,\ldots, w_N)^T$ is weights of the model are obtained during training.
Here are the results of calculations for different methods of text vectorization.
The results for BOW and Fast Text embeddings, are introduced in table\,\ref{tbl:01}.
\begin{table}
	\centering
	\caption{\label{tbl:01}Training result.}
	\begin{center}
		\begin{tabular}{lll}
			\br
			embeddings & precision & recall \\
			\mr
			BOW & 0.91143 & 0.99961 \\ \hline
			Fast Text & \bf 0.95523 & \bf 0.89164 \\ 
			\br
		\end{tabular}
	\end{center}
\end{table}

\subsubsection{Fully convolutional neural network}
The fully convolutional neural network with 3 layers was considered. The first two use the \textsf{ReLU} activation function, and the last one uses \textsf{sigmoid}. Data is regularized on each layer. In our case, the neural network can be defined by the formula
$$
g(x) = h_2 \left(\sum_{k=0}^{n_2} w''_k h_1\left(\sum_{j=0}^{n_1} w'_j h_0\left( \sum_{i=0}^{n_0} w_i x_i \right)\right)\right),
$$
where $h_i$ is the activation function for the corresponding layer. To find the weights $\{w_i\}$, $\{w'_j\}$, $\{w''_k\}$ at the model training stage, the Adam method is used.
The results for BOW and Fast Text embeddings, are also introduced in table\,\ref{tbl:02}.
\begin{table}
	\centering
	\caption{\label{tbl:02}Training result.}
	\begin{center}
	\begin{tabular}{lll}
		\br
		embeddings & precision & recall \\
		\mr
		BOW & 0.93604 & 0.95643 \\ \hline
		Fast Text & \bf 0.99931 & \bf 0.91263 \\ 
		\br
	\end{tabular}
	\end{center}
\end{table}

\subsection{Aspects of algorithm implementation}
\subsubsection{Microservice architecture}
Since the service must operate under high loads, it is important to provide an architecture in which the failure of one component does not lead to the degradation of the entire system. The following client-server architecture is implemented (Fig. 1). Antispam daemon (mrasd) parses incoming messages and extracts text, images, and files from there. Since unwanted data is often contained inside nested images and documents, it is also necessary to extract text from them. To do this, the documents are sent to the OCR service via a deferred redis queue, which extracts the text and stores the result in the redis cache.

Since, with a high probability, the letter can be a duplicate (for example, in the case of a ddos attack or offline rechecking), in order not to load the OCR service once again, the primary check of the redis cache is performed for the presence of already processed data for the specified document hash.

After full text extraction, the mrasd service performs all the steps of text preprocessing (reduction to a single register, removal of stop words, normalization), and then sends the text to the mlapi service via the grpc protocol to vectorize the text using fast text and further obtain the fcnn prediction of the model by which a decision is made about the" undesirability " of the incoming message.

The proposed architecture is good because when the OCR of seris, one (or several) instances of redis cluster fails, the entire system as a whole does not degrade.

\begin{figure}[h!]
	\center
	\includegraphics[scale=0.25]{images/deploy.jpg}
	\caption{\label{fig:02} Deploy}
\end{figure}

\begin{figure}[h!]
	\center
	\includegraphics[scale=0.6]{images/timings.png}
	\caption{\label{fig:03} Average email processing time}	
\end{figure}

\begin{figure}[h!]
	\center
	\includegraphics[scale=0.5]{images/processed_messages.png}
	\caption{\label{fig:04} Average number of requests per minute from one of the farms}
\end{figure}

\subsubsection{Brief review of the libraries}

Since services require high performance, the C++ language (stl 17, grpc, boost) is chosen for writing it, as one of the most productive modern languages. For data analysis and training of the AST model, the Python 3 language and the utouch framework were used due to the high efficiency and the possibility of conducting parallel calculations, both on the CPU and on the GPU cores of the machine.

The fault tolerance of microservices is ensured by their deployment in the kubernetes (k8s) cluster, since if any pod falls for any reason, the requests are evenly balanced across the remaining live feeds, until the cluster independently returns to its previous state. Inside it, you can configure: automatic load balancing by constantly monitoring information about performance and resources used (autoscaling) and competent placement of hearths within the cluster by data centers (affinity).

@@

The results obtained during the training of the model on real streaming data of users are introduced. Based on these data, one can realize that \textsf{FCNN} model based on Fast Text embeddings has higher classification accuracy rather then method of classical logistic regression and \textsf{FCNN}  model based on a bag of words.

@@

\begin{thebibliography}{99}
\bibitem{Makkar2021} 
Aaisha Makkar, Uttam Ghosh, Pradip Kumar Sharma.
2021. \emph{Artificial Intelligence and Edge Computing-enabled
	Web Spam Detection for Next Generation IoT
	Applications} // IEEE Sensors Journal

@@

\bibitem{Mohammad2020}
Rami Mustafa A. Mohammad.
2020. \emph{A lifelong spam emails 	classification model} //
Applied Computing and Informatics
\end{thebibliography}

>>>>

\section{Methodology}
\subsection{Statement of the problem}
Let's consider a set of objects $ X = X_L \cup X_T$, where
$X_L$ is training sample,
$X_T$ is test sample,
$Y$ is set of valid responses. Also, assume that there is an objective function $g: X \rightarrow Y$, whose values are known only on the set $X_L$. Let the data be distributed according to some unknown distribution $P (x,y) = P(x) P (y|x)$, with some loss function given
$$
R(g(x), y) = 
\begin{cases} 
\phantom{>}0, & y = g(x), \\
> 0, & y \neq g(x).
\end{cases}
$$
In accordance with the principle of minimizing empirical risk, the loss function is used to be minimazied. In other words a decision function $g(x)$, which on average will lead to the smallest error is determined. Formally, one need to solve the minimization problem as follows
$$
g(x) = \operatorname*{argmin}_{f: X \rightarrow Y} E_{X,Y} R(f(x), y).
$$
To state the problem of junk data filtration, the set $Y$ consists of two elements $\{0, 1\}$, where $0$ and $1$ are desirable and undesirable data, respectively. Due to the roughness of the discrete computing methods $R = P[0, 1]$ is usually used in practice. Thus, the result of the classifier $r' = r(x)$ belongs to the desired class with a given threshold probability $\alpha$, which minimizes the error of the first and second kind.

@@

\subsection{Text processing}
Since the text has a very heterogeneous structure and a single word can be written in many different ways (different font, encoding, case, etc.), but still have the same meaning, different methods of tesxts preprocessing or combination of them are considered.

The first step of preprocessing is to parse the text and decode it into the specified encoding. Then it is conversed to the lower (or upper) case, unnecessary spaces and indents are removed. The characters are replaced according to the specified rule. Further, some methods of text processing are introduced below.

\subsubsection*{Stop words.}
The text often contains many characters that don't have any semantic sence for the general meaning (two spaces, paragraph indentation).
Similarly, stop words are the words in any language that don't have much sence in a sentence. Often, stop words include punctuation marks, pronouns, and prepositions. Often, spammers use them to make texts noisy in order to hide the spam content of the message. Since they can be safely ignored without sacrificing the meaning of the sentence, classification tasks often resort to removing them from the original message.

\subsubsection*{Stemming and lemmatization.}
Usually texts contain different grammatical forms of the same word, and may also contain the same root words. Using different algorithms, lemmatization and stemming aim to reduce all occurring word forms to a single, normal dictionary form.

Stemming is a crude heuristic process which cuts off ``extra'' from the word root, often resulting in a loss of word--formation suffixes. The main problem encountered when using stemming is the processing of words which, when forming different grammatical forms, change not only the ending, but also the base of the word. To minimize the negative consequences of too aggressive truncation of words by the streamer, it is necessary to perform memming of the searched keyword, and then compare the result with the output of the streamer for each of the words in the processed text.

Lemmatization is a more subtle process, which uses dictionary and morphological analysis to reduce a word to its canonical form (lemma). However, it applies simplistic word analysis without considering the context. This leads to ambiguities in determining parts of speech. This ambiguity cannot be resolved without involving the morphological analyzer.

Basically, lemmatization gives the most accurate results, and it is utilized in the proposed approach.

\subsection{Text vectorization}
Modern machine learning algorithms are not able to process raw text directly, so it is necessary to develop a map from text to a vector space. This is called feature extraction. 
Let's consider several approaches allows to construct this map below.

\subsubsection*{Bag of words.}
The ``bag of words'' (BOW) model is a simplified representation of text used in natural language processing and information retrieval problems. Text is considered as a bag (multiset) of words or phrases in the case of combinations of terms, ignoring grammar and in some cases even word order, but preserving multiplicity in BOW. Each term (word or phrase) is assigned with a number. Then, text is defined by the vector $x=(x_1,..., x_N)^T$, where $N$ is the dimension from the finite dictionary $X_L$ contains the unique terms of the training sample. The following options to define $x_i$ are possible
\begin{enumerate}
\item Boolean weight equals $1,$ if element exists in a message or 
$0,$ else.
\item The number of occurrences of the $i$--th term in the text is 
$x_i = n_i.$
\item Term frequency is $x_i = n_i\slash\left(\sum\limits_{k=1}^i n_k\right).$
\end{enumerate}
{\color{red}\bf To determine $x_i$, the frequency of the term is selected.}

\subsubsection*{Word2Vec.}
The main problem of BOW model is the loss of context between words. Since in natural language, the permutation of even two words of a sentence can completely change the meaning, this classification approach may have low accuracy.
Word2Vec is a text vectorization tool that takes into account the contextual relationship between words. The algorithm is based on huffman binary tree, skip--gram, negative sampling approaches. The bottle-necked place in Word2Vec is to find the context for the rare words.

\subsubsection*{Fast Text.}
FastText is a Word2Vec extension proposed by Facebook in 2016 {\bf\color{red}[ref01] \cite{Ref01}}. Fast Text approach splits the words into several n--grams (proverbs) Instead of considering individual words as an input of a neural network. After training the neural network, the embedding words for all n--grams from the training dataset arise.
Applying such an approach, the solution becomes more sensitive to rare words, since it is highly likely that some of their n--grams are also presented in other words. Training the Fastext model takes longer time, but it works more precise than Word2Vec and allows to  represent rare words correctly.

\subsection{Text classification}
After text vectorization, a transform from a set of features to a set of classifiable objects $g: X \rightarrow Y$ is developed.
According to the article {\bf\color{red}[ref: twitter threshold p. 4.6]\cite{Ref02}}, unique points were marked by bins and the optimal threshold accuracy $\alpha = 0.75$ was calculated, which provides optimal pressision and recall for our model and minimizes the error variance.

\subsubsection*{Logistic regression.}
The common approach in the classification is to apply the logistic regression method
$$
g(x) = \left(1 + \exp{ \left( \sum_{i=0}^n w_i x_i  \right) }\right)^{-1},
$$
where $\mathbf{w}=(w_1,\ldots, w_N)^T$ are weights of the model arised in training process.

Two different methods of text vectorization were examined experimentaly.
The results for BOW and Fast Text embeddings, are introduced in table\,\ref{tbl:01}.

\begin{table}[h!]
	\centering
	\caption{\label{tbl:01}Training result.}
	\begin{center}
		\begin{tabular}{lll}
			\br
			embeddings & precision & recall \\
			\mr
			BOW & 0.91143 & 0.99961 \\ \hline
			Fast Text & \bf 0.95523 & \bf 0.89164 \\ 
			\br
		\end{tabular}
	\end{center}
\end{table}

\subsubsection*{Fully convolutional neural network (FCNN).}
The fully convolutional neural network with 3 layers was considered. A \textsf{ReLU} activation function was applied to the first and second layersthird, and the last one utilize \textsf{sigmoid} as an activation function. Data was regularized on each layer. Neural network can be defined as follows in our case
$$
g(x) = h_2 \left(\sum_{k=0}^{n_2} w''_k h_1\left(\sum_{j=0}^{n_1} w'_j h_0\left( \sum_{i=0}^{n_0} w_i x_i \right)\right)\right),
$$
where $h_i$ is the activation function for the corresponding layer. Adam method is utilized to find weights $\{w_i\}$, $\{w'_j\}$, $\{w''_k\}$ at the model training stage.
The results for BOW and Fast Text embeddings, are also introduced in table\,\ref{tbl:02}.
\begin{table}[h!]
	\centering
	\caption{\label{tbl:02}Training result.}
	\begin{center}
	\begin{tabular}{lll}
		\br
		embeddings & precision & recall \\
		\mr
		BOW & 0.93604 & 0.95643 \\ \hline
		Fast Text & \bf 0.99931 & \bf 0.91263 \\ 
		\br
	\end{tabular}
	\end{center}
\end{table}

\subsection{Aspects of algorithm implementation}
\subsubsection*{Microservice architecture.}
Since the service must operate under high loads, it is important to provide a robust architecture in which the failure of one component does not lead to the degradation of the entire system. The following client--server architecture is shown in figure\,\ref{fig:01}. Antispam daemon (mrasd) parses incoming messages and extracts text, images, and files from there. Since nested images and documents often contain junk data, it is also necessary to extract text from them. Then, documents are sent to the OCR service via a deferred redis queue, which extracts the text and stores the result in the redis cache.

\begin{figure}[t]
	\center
	\includegraphics[width=0.95\textwidth]{images/deploy.jpg}
	\caption{\label{fig:01} Deploy}
\end{figure}

\begin{figure}[b]
	\center
	\includegraphics[width=0.95\textwidth]{images/timings.png}
	\caption{\label{fig:02} Average email processing time}	
\end{figure}

Since, highly likely the letter can be duplicated (for example, in the case of a ddos attack or offline rechecking), in order not to load the OCR service once again, the primary check of the redis cache is performed for the presence of already processed data for the specified document hash.

After full text extraction, the mrasd service performs all the steps of text preprocessing (reduction to a single register, removal of stop words, normalization), and then sends the text to the mlapi service via the grpc protocol to vectorize the text using fast text and further obtain the fcnn prediction of the model by which a decision is made about the ``undesirability'' of the incoming message.

The proposed architecture is fairly robust because when the OCR of seris, one (or several) instances of redis cluster fails, the entire system as a whole does not degrade.

\begin{figure}[t]
	\center
	\includegraphics[width=0.95\textwidth]{images/processed_messages.png}
	\caption{\label{fig:03} Average number of requests per minute from one of the farms}
\end{figure}

\subsubsection*{Brief review of the libraries}
Since services require high performance, the C++ language (stl 17, grpc, boost) is chosen as one of the most productive modern languages. For data analysis and training of the {\bf\color{red}AST model}, the Python 3 language and the utouch framework were utilized due to the high efficiency and the possibility of conducting parallel calculations, both on the CPU and on the GPU cores of the machine.

The fault tolerance of microservices is ensured by their deployment in the kubernetes (k8s) cluster, since if any pod falls for any reason. The requests are evenly balanced across the remaining live feeds, until the cluster independently returns to its previous state.

@@

The results obtained during the training of the model on real--life streaming data of users are introduced. Based on these data, one can realize that FCNN model based on Fast Text embeddings has higher classification accuracy rather then method of classical logistic regression and FCNN  model based on a bag of words.

@@

\section*{References}
\begin{thebibliography}{99}
\bibitem{Makkar2021} 
Aaisha Makkar, Uttam Ghosh, Pradip Kumar Sharma.
2021. \emph{Artificial Intelligence and Edge Computing-enabled
	Web Spam Detection for Next Generation IoT
	Applications} // IEEE Sensors Journal

@@

\bibitem{Mohammad2020}
Rami Mustafa A. Mohammad.
2020. \emph{A lifelong spam emails 	classification model} //
Applied Computing and Informatics

\bibitem{Ref01} 
{\bf\color{red} Ref01}

\bibitem{Ref02} 
{\bf\color{red} Ref02}
\end{thebibliography}
